jk test with big K, balanced label

### 2016-10-20 Rmd/convergenceRatesImbalancedBigK.Rmd
ordered Mu after clustering is done, before passing back to R

mu0<- c(1:K)
mu<- matrix( 0,n*K,p)
mu <- rep(mu0, each = n)
sigma<-  0.5

@@

Here is a view of the two clusters
```{r}

@@

functions to compute misclassification error and rmse of mean estimate:
NB: GMM can get stuck in saddle point at (w1=0, w2=1), so I removed the test result when it happened.
```{r}
computeMError<- function(jk, n,batchN){
  error<- numeric(batchN)
  for(b in 1:batchN){
    tM0<- rank(jk$mu[,1,b])-1
    trueM<- rep(tM0,each=n)
    error[b]<- sum ( jk$M[,b] != trueM) /K/n
    if( min(jk$w[,b])<0.01){
      error[b]<- NA
    }
  }
  error
}

computeRMSE<- function(jk, mu0, batchN){
  rmse<- numeric(batchN)
  for(b in 1:batchN){
    newOrder<- order(jk$mu[,1,b],decreasing = F)

    muEst<-as.matrix(jk$mu[,,b])[newOrder,]

    rmse[b]<- sqrt( mean((muEst - mu0)^2))
    if( min(jk$w[,b])<0.01)
      rmse[b]<- NA
  }
  rmse
}

@@

  p<- 1
  batchN<- 1000

@@

  mu0<- c(1:K)
  mu<- matrix( 0,n*K,p)
  mu <- rep(mu0, each = n)

@@

  error<- sapply(runRes,function(x){computeMError(x,n,batchN)})
  rmse<- sapply(runRes,function(x){computeRMSE(x,mu0,batchN)})

@@

nSeries<- c(seq(20,500,by = 20))

@@

  save(result, file="resultRatesBigK.Rda")
}

@@

```{r include=FALSE}

nSeries<- c(seq(20,500,by = 20))

BEsim<- function(n){
  p<- 1
  batchN<- 1000

  mu0<- c(1:K)
  mu<- matrix( 0,n*K,p)
  mu <- rep(mu0, each = n)

  dist<- abs(outer(c(yBatch), mu0, "-"))
  bayesclassified <- apply(dist, 1, function(x){c(1:K)[x==min(x)]})
  #bayes error
  (sum(bayesclassified != rep(c(1:K),each=n))/n/K/batchN)
}

bayesErorr<- BEsim(100)

@@

load("resultRatesBigK.Rda")

@@

>>>>

mu0<- c(1:K)
# mu<- matrix( 0,n*K,p)
# mu <- rep(mu0, each = n)

mu<- c(rep(1,n*3/2), rep(2, n/2),  rep(3, n/2*3), rep(4,n/2), rep(5,n))

sigma<-  0.5

@@

Here is a view of the clusters
```{r}

@@

functions to compute misclassification error and rmse of mean estimate:
NB: GMM can get stuck in saddle point at (w1=0, w2=1), so I removed the test result when it happened.
```{r}
computeMError<- function(jk, batchN, trueM){
  error<- numeric(batchN)
  for(b in 1:batchN){
    # tM0<- rank(jk$mu[,1,b])-1
    # trueM<- rep(tM0,each=n)
    error[b]<- mean ( jk$M[,b] != (trueM -1 ))
    if( min(jk$w[,b])<0.01){
      error[b]<- NA
    }
  }
  error
}

computeRMSE<- function(jk, batchN, trueMu){
  rmse<- numeric(batchN)
  for(b in 1:batchN){
    newOrder<- order(jk$mu[,1,b],decreasing = F)
    muEst<-as.matrix(jk$mu[,,b])[newOrder,]

    rmse[b]<- sqrt( mean((muEst - trueMu)^2))
    if( min(jk$w[,b])<0.01)
      rmse[b]<- NA
  }
  rmse
}

@@

  p<- 1
  batchN<- 100

@@

  mu0<- c(1:K)
  mu<- c(rep(1,n*3/2), rep(2, n/2),  rep(3, n/2*3), rep(4,n/2), rep(5,n))

  trueM<- mu #same as mu
  trueMu<- mu0

@@

  error<- sapply(runRes,function(x){computeMError(x,batchN, trueM)})
  rmse<- sapply(runRes,function(x){computeRMSE(x,batchN, trueMu)})

@@

nSeries<- c(seq(20,200,by = 20),300,400,500)

@@

  save(result, file="resultRatesImbalancedBigK.Rda")
}

@@

```{r include=FALSE}
# 
# nSeries<- c(seq(20,500,by = 20))
# 
# 
# 
# BEsim<- function(n){
#   p<- 1
#   batchN<- 1000
#   
#   yBatch<- array(0,dim = c(n*K,p,batchN))
#   
#   mu0<- c(1:K)
#   mu<- matrix( 0,n*K,p)
#   mu <- rep(mu0, each = n)
#   
#   for(b in 1:batchN){
#     yBatch[,,b]<- matrix( rnorm(n*p*K,mu,sigma), n*K, p)
#   }
#   
#   dist<- abs(outer(c(yBatch), mu0, "-"))
#   bayesclassified <- apply(dist, 1, function(x){c(1:K)[x==min(x)]})
#   #bayes error
#   (sum(bayesclassified != rep(c(1:K),each=n))/n/K/batchN)
# }
# 
# 
# bayesErorr<- BEsim(100)

@@

load("resultRatesImbalancedBigK.Rda")

@@

# p+ geom_errorbar( aes(x=n,ymax = MC14ErrorU, ymin=MC14ErrorL, colour=Model),width=0.2)
p+ theme_bw() #+ geom_hline(yintercept = bayesErorr)
# pE + theme_bw()
```
